Nail: A practical interface generator for data formats

### 2014-05-02 paper/osdi14/intro.tex
Added CVE bugs

Third, many data formats contain redundancies, such as repeating
information in multiple structures.  Applications usually do not
explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that
causes inconsistencies~\cite{cve-python-zip-maybe}.  Furthermore, security
vulnerabilities can occur when an application assumes two repetitions
of the same data to be consistent, such as allocating a buffer based on
the value of one size field and copying into that buffer based on the
value of another~\cite{cve-some-example}.

>>>>

Third, many data formats contain redundancies, such as repeating
information in multiple structures.  Applications usually do not
explicitly check for consistency, and if different applications use
different instances of the same value, an attacker can craft input that
causes inconsistencies~\cite{evaders6}.  Furthermore, security
vulnerabilities can occur when an application assumes two repetitions
of the same data to be consistent, such as allocating a buffer based on
the value of one size field and copying into that buffer based on the
value of another~\cite{cve-2012-7338}.
